An Example Article

### 2023-06-06 article-en/article-temp-info.tex
update

% hyperlink setting
\hypersetup{
  colorlinks = true,
  linkcolor = magenta,
  citecolor = blue,
  filecolor = blue,
  urlcolor = blue,
}

@@

% layout setting
\usepackage{geometry}
\geometry{left=1.25in,right=1.25in,top=1.25in,bottom=1.25in}
%\setlength{\textwidth}{15cm}
%\setlength{\textheight}{21.6cm}
%\setlength{\oddsidemargin}{0.5cm}
%\setlength{\evensidemargin}{0.5cm}

\makeatletter
\newcommand\@shorttitle{}
\newcommand\shorttitle[1]{\def\@shorttitle{#1}}
\newcommand\@shortauthor{}
\newcommand\shortauthor[1]{\def\@shortauthor{#1}}
\makeatother

% headers and footers setting
%\pagestyle{fancy}
%\fancyhf{}
%\fancyhead[CO]{\footnotesize\uppercase{Title of Paper}}
%\fancyhead[CE]{\footnotesize\uppercase{Author A, Author B \& Author C}}
%\fancyfoot[C]{\footnotesize\thepage}
%\renewcommand{\headrulewidth}{0pt}

%\fancyhead[C]{\footnotesize\uppercase{Title of Paper}}
%\fancyfoot[C]{\footnotesize\thepage}
%\renewcommand{\headrulewidth}{0pt}

\makeatletter
\pagestyle{fancy}
\fancyhf{}
\fancyhead[CO]{\footnotesize\MakeUppercase{\@shorttitle}}
\fancyhead[CE]{\footnotesize\MakeUppercase{\@shortauthor}}
\fancyhead[RO]{\footnotesize\thepage}
\fancyhead[LE]{\footnotesize\thepage}
\renewcommand{\headrulewidth}{0pt}
\makeatother

@@

% redefine maketitle environment
\makeatletter
\def\@maketitle{%
  \newpage
  \null
  %\vspace{-1.5em}%
  \begin{center}%
    \let \footnote \thanks
    {\Large \bfseries \@title \par}%
    \vskip 1.5em%
    {\large
      \lineskip 0.5em%
      \begin{tabular}[t]{c}%
        \@author
      \end{tabular}\par}%
    \vskip 0.5em%
    {\large \@date}%
  \end{center}%
  \par
  \vskip 1em
}
\makeatother

@@

% Short title for running heads:
\shorttitle{A posteriori error analysis for CG methods for PDDEs}

\author[1]{Author A}
\author[2]{Author B}
\author[1]{Author C\thanks{Email address: \texttt{xyz@math.univ.edu}; Corresponding author.}}
\affil[1]{Department of Mathematics, \LaTeX\ University}
\affil[2]{Department of Mechanical Engineering, \LaTeX\ University}

>>>>

% hyperlink setting
\hypersetup{
  colorlinks=true,
  linkcolor=magenta,
  citecolor=blue,
  filecolor=blue,
  urlcolor=blue
}

@@

% layout setting
\usepackage{geometry}
\geometry{left=1.25in,right=1.25in,top=1.25in,bottom=1.25in}
\setlength{\headheight}{18pt}
\setlength{\headsep}{18pt}
\setlength{\footskip}{25pt}
%\setlength{\textwidth}{15cm}
%\setlength{\textheight}{21.6cm}
%\setlength{\oddsidemargin}{0.5cm}
%\setlength{\evensidemargin}{0.5cm}

% define some new commands
\makeatletter
\newcommand\cortext[1]{\def\@cortext{#1}}
\newcommand\shorttitle[1]{\def\@shorttitle{#1}}
\newcommand\shortauthor[1]{\def\@shortauthor{#1}}
\makeatother

\newcommand\cormark{\raisebox{-1.6pt}{*}}
\newcommand\blfootnote[1]{%
  \begingroup
  \renewcommand\thefootnote{}\footnote{#1}%
  %\addtocounter{footnote}{-1}%
  \endgroup
}

% headers and footers setting
\makeatletter
\pagestyle{fancy}
\fancyhf{}
\fancyhead[CO]{\footnotesize\MakeUppercase{\ifx\@shorttitle\undefined{}\else\@shorttitle\fi}}
\fancyhead[CE]{\footnotesize\MakeUppercase{\ifx\@shortauthor\undefined{}\else\@shortauthor\fi}}
\fancyhead[RO]{\footnotesize\thepage}
\fancyhead[LE]{\footnotesize\thepage}
\renewcommand{\headrulewidth}{0pt}
\makeatother

@@

% redefine maketitle environment
\makeatletter
\def\@maketitle{%
  \newpage
  \null
  %\vspace{-1.5em}%
  \begin{center}%
    \let \footnote \thanks
    {\Large \bfseries \@title \ifx\@cortext\undefined{}\else\blfootnote{\@cortext}\fi \par}%
    \vskip 1.5em%
    {\large
      \lineskip 0.5em%
      \begin{tabular}[t]{c}%
        \@author
      \end{tabular}\par}%
    \vskip 0.5em%
    {\large \@date}%
  \end{center}%
  \par
  \vskip 1em
}
\makeatother

@@

% Short title for running heads:
\shorttitle{Short Title of the Article}

\author[1]{Author A}
\author[2]{Author B}
\author[1,\cormark]{Author C}
\affil[1]{Department of Mathematics, \LaTeX\ University}
\affil[2]{Department of Mechanical Engineering, \LaTeX\ University}
\cortext{Corresponding author. Email address: \texttt{xyz@math.univ.edu}}
